Append_smoothed_results

### 2017-06-02 Code/archived/old_2_Run_LE_and_Decomp_Calcs.Rmd

rm(les, le1, le5, le9)
```

@@

save(paired.ids, non.zero.stratums,
     list.age.decomp.tables1, list.age.decomp.tables5, list.age.decomp.tables9,
     list.life.tables1, list.life.tables5, list.life.tables9,  
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/calculated_data.Rdata")
```

@@

        list.cod.decomp.tables9[[i]]$decomp.table <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables5[[black.index]]$life.table),
                                                              life.table2 = as.data.frame(list.life.tables5[[white.index]]$life.table), 
                                                              decomp.table = as.data.frame(list.age.decomp.tables5[[i]]$decomp.table),
                                                              cod.table = ct.both %>% select(age, COD, prop.white9, prop.black9), 
                                                              age.colname.cod.table = "Age_factor", 
                                                              COD.colname.cod.table = "COD_factor", 
                                                              prop1.colname.cod.table = "prop.black9", 
                                                              prop2.colname.cod.table = "prop.white9")

@@

```{r  update_decomp_for_plotting}
#update the decomposition table for plotting purposes
for(i in 1:dim(paired.ids)[1]) {
    if(list.cod.decomp.tables[[i]][1] != "Couldn't compare life tables" & 
       list.cod.decomp.tables[[i]][1] != "Encountered age group with no deaths") {

       list.cod.decomp.tables[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables1[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death", 
                                                            sign.var = "sign", decomp.var = "C_xi", 
                                                            decomp.var.prop = "C_xi_proportion")

       list.cod.decomp.tables5[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables5[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death", 
                                                            sign.var = "sign", decomp.var = "C_xi", 
                                                            decomp.var.prop = "C_xi_proportion")

       list.cod.decomp.tables9[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables9[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death", 
                                                            sign.var = "sign", decomp.var = "C_xi", 
                                                            decomp.var.prop = "C_xi_proportion") 
    } 
  print(i)
}  
```

```{r pretty_cod}
ggplot(list.cod.decomp.tables[[1]], aes(y = Ages, x = start)) + 
  geom_segment(aes(xend = finish, col = Cause.of.death, yend = Ages), lwd = 4) +
  xlab("Contribution to life expectancy gap") +
  ylab("Age group\n") + theme_minimal() +
  geom_vline(xintercept = 0)

ggplot(list.cod.decomp.tables9[[1]], aes(y = Ages, x = start)) + 
  geom_segment(aes(xend = finish, col = Cause.of.death, yend = Ages), lwd = 4) +
  xlab("Contribution to life expectancy gap") +
  ylab("Age group\n") + theme_minimal() +
  geom_vline(xintercept = 0)
```

>>>>

rm(les, le1, le5, le9, sid)
```

@@

@@

        list.cod.decomp.tables9[[i]]$decomp.table <- cause_of_death_decomp(life.table1 = as.data.frame(list.life.tables5[[black.index]]$life.table),
                                                              life.table2 = as.data.frame(list.life.tables5[[white.index]]$life.table), 
                                                              decomp.table = as.data.frame(list.age.decomp.tables5[[i]]$decomp.table),
                                                              cod.table = ct.both %>% select(age, COD, prop.white9, prop.black9), 
                                                              age.colname.cod.table = "age", 
                                                              COD.colname.cod.table = "COD", 
                                                              prop1.colname.cod.table = "prop.black9", 
                                                              prop2.colname.cod.table = "prop.white9")

@@

```{r  update_decomp_for_plotting}
#update the decomposition table for plotting purposes
for(i in 1:dim(paired.ids)[1]) {
    if(list.cod.decomp.tables1[[i]]$decomp.table[1] != "Couldn't compare life tables" & 
       list.cod.decomp.tables1[[i]]$decomp.table[1] != "Encountered age group with no deaths") {

       list.cod.decomp.tables1[[i]]$decomp.table <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables1[[i]]$decomp.table,
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death", 
                                                            sign.var = "sign", decomp.var = "C_xi", 
                                                            decomp.var.prop = "C_xi_proportion")

       list.cod.decomp.tables5[[i]]$decomp.table <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables5[[i]]$decomp.table,
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death", 
                                                            sign.var = "sign", decomp.var = "C_xi", 
                                                            decomp.var.prop = "C_xi_proportion")

       list.cod.decomp.tables9[[i]]$decomp.table <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables9[[i]]$decomp.table,
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death", 
                                                            sign.var = "sign", decomp.var = "C_xi", 
                                                            decomp.var.prop = "C_xi_proportion") 
    } 
  print(i)
}  
```

```{r pretty_cod}
ggplot(list.cod.decomp.tables1[[1]]$decomp.table, aes(y = Ages, x = start)) + 
  geom_segment(aes(xend = finish, col = Cause.of.death, yend = Ages), lwd = 4) +
  xlab("Contribution to life expectancy gap") +
  ylab("Age group\n") + theme_minimal() +
  geom_vline(xintercept = 0)

ggplot(list.cod.decomp.tables9[[1]]$decomp.table, aes(y = Ages, x = start)) + 
  geom_segment(aes(xend = finish, col = Cause.of.death, yend = Ages), lwd = 4) +
  xlab("Contribution to life expectancy gap") +
  ylab("Age group\n") + theme_minimal() +
  geom_vline(xintercept = 0)
```

save(paired.ids, non.zero.stratums,
     list.life.tables1, list.life.tables5, list.life.tables9,  
     list.age.decomp.tables1, list.age.decomp.tables5, list.age.decomp.tables9,
     list.cod.decomp.tables1, list.cod.decomp.tables5, list.cod.decomp.tables9,
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/calculated_data.Rdata")
```

### 2017-06-02 Code/archived/old_append_smoothed_results.Rmd

BlackWhite$Census_Region[BlackWhite$State2 %in% c("Alabama", "Kentucky", "Mississippi", "Tennessee", 
                                                  "Arkansas", "Louisiana", "Oklahoma", "Texas")] <- "West or East South Central"

@@

@@

cod.contributions$Census_Region[cod.contributions$State2 %in% c("Alabama", "Kentucky", "Mississippi", "Tennessee", 
                                                                "Arkansas", "Louisiana", "Oklahoma", "Texas")] <- "West or East South Central"

>>>>

BlackWhite$Census_Region[BlackWhite$State2 %in% c("Alabama", "Kentucky", "Mississippi", "Tennessee", 
                                                  "Arkansas", "Louisiana", "Oklahoma", "Texas")] <- "South Central"

BlackWhite$Census_Region <- factor(BlackWhite$Census_Region, levels = c("West", "Midwest", "South Central", "South Atlantic", "Northeast"))

@@

cod.contributions$State2 <- factor(cod.contributions$State2, levels = c("Alabama", "Arizona", "Arkansas",
                                                                        "California", "Colorado", "Connecticut",
                                                                        "Delaware", "Washington DC", "Florida", "Georgia", "Illinois",
                                                                        "Indiana", "Iowa", "Kansas", "Kentucky", 
                                                                        "Louisiana", "Maryland", "Massachusetts", 
                                                                        "Michigan", "Minnesota", "Mississippi",
                                                                        "Missouri", "Nebraska", "Nevada", "New Jersey", 
                                                                        "New Mexico", "New York", "North Carolina", 
                                                                        "Ohio", "Oklahoma", "Pennsylvania", "Rhode Island", 
                                                                        "South Carolina", "Tennessee", "Texas", "Utah", 
                                                                        "Virginia", "Washington", "West Virginia", "Wisconsin" ))

@@

cod.contributions$Census_Region[cod.contributions$State2 %in% c("Alabama", "Kentucky", "Mississippi", "Tennessee", 
                                                                "Arkansas", "Louisiana", "Oklahoma", "Texas")] <- "South Central"

cod.contributions$Census_Region <- factor(cod.contributions$Census_Region, levels = c("West", "Midwest", "South Central", "South Atlantic", "Northeast"))

cod.contributions$rand_year = 2000 + sample(0:10, 1) #used for jittering labels on the plot 
```
